Three 38 Million Year Old Mini-Neptunes from Kepler, TESS, and Gaia

### 2022-03-02 papers/ms.tex
update rotation and lithium plots

%% Reintroduced the \received and \accepted commands from AASTeX v5.2.
%% Add "Submitted to " argument.
\received{2021 Oct 12}
\revised{---}
\accepted{---}
%\submitjournal{AAS Journals}
\shorttitle{Kepler Mini-Neptunes in Cep-Her}

@@

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.99\textwidth]{f1.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Galactic positions  and tangential velocities of stars in the
    complex.} 
    Sub-clusters include the $\delta$ Lyr cluster, RSG-5, and the
    worryingly diffuse ``CH-2''.
		\label{fig:XYZvtang}
	}
\end{figure*}

@@

		\vspace{-0.6cm}
		\subfloat{
			\includegraphics[width=0.49\textwidth]{f2c.pdf}
			\includegraphics[width=0.49\textwidth]{TEMP_f2d.pdf}
		}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf The \cn\ is \clusterage\ old.} 
    The top row shows CAMDs.  Left shows CH-2, right shows RSG-5.
    The bottom left shows gyro.
    The bottom right shows lithium (and is a {\bf place-holder}).  (Somewhere we will have
    H-alpha?).
		\label{fig:age}
	}
\end{figure*}

>>>>

%% Reintroduced the \received and \accepted commands from AASTeX v5.2.
%% Add "Submitted to " argument.
\received{\today}
\revised{---}
\accepted{---}
%\submitjournal{AAS Journals}
\shorttitle{Kepler Mini-Neptunes in Cep-Her}

@@

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.99\textwidth]{f1.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Galactic positions  and tangential velocities of stars in the
    complex.}  {\bf This is a placeholder before we get real kinematics.}
    Sub-clusters include the $\delta$ Lyr cluster, RSG-5, and the
    worryingly diffuse ``CH-2''.
		\label{fig:XYZvtang}
	}
\end{figure*}

@@

		\vspace{-0.6cm}
		\subfloat{
			\includegraphics[width=0.49\textwidth]{f2c.pdf}
			\includegraphics[width=0.49\textwidth]{f2d.pdf}
		}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf The \cn\ is \clusterage\ old.} 
    The top row shows CAMDs.  Left shows CH-2, right shows RSG-5.
    The bottom left shows gyro (and is a {\bf place-holder since we might want to add CH-2 and RSG5}).
    The bottom right shows lithium (black points are NGC2547 and
    IC2602 from Randich+18 and probably are not believable at the red
    end; for Kepler-1643 I'm less confident, but it might be tied to the ``slow'' rotation period -- this is why we need RSG5 rotation periods).
    Also, we might want an
    H-alpha plot?).
		\label{fig:age}
	}
\end{figure*}
